Characterizing edges in signed and vector-valued graphs

### 2017-12-18 cc/cc_variants.tex
pass over CC

Bipartite graphs are an interesting special case for \pcc{}, as they often appear in the context of
recommendation systems, where users rate products positively or negatively, although in this setting
we cannot expect to have complete bipartite graphs in practice. The first results was given by
\textcite{Amit04}, who obtains an $11$-approximation for \mind{} by adapting the \regionGrow{} method.
The \ccpivot{} is adapted to the bipartite case by
\textcite{Bipartite12}, who prove it results in a randomized $4$-approximation (and provide a matching
deterministic approximation by rounding a LP). By using their idea of rounding the results of the LP
differently for positive, negative and in that case same-side absent edges, \textcite{Chawla2014}
bring down this approximation factor to $3$, even for $K\geq 2$-partite graphs. Through formulating the
\maxa{}$[k]$ problem as a bilinear maximization problem and computing a low-rank approximation of
the graph biadjacency matrix, \textcite{Asteris2016} obtain a efficient PTAS, that is a $(1-\delta)$
approximation running in time exponential in $k$ and $\delta^{-1}$ but linear in $n$. By an
appropriate choice of $k$, it is possible to use this PTAS to solve the general \maxa{} problem.

@@

In the so called \textsc{Chromatic}-\pcc{} setting, \enquote{positive} edges are now associated with
one of $L$ possible colors and the goal is to form clusters mostly made up of edges with the one same
color. Namely, a disagreement is now a negative edge between clusters or a within-cluster edge
whose color differs from the majority color of that cluster. This is motivated by edge-labeled graph
in social networks, biology and citation networks and will discuss such applications in
\autoref{chap:vector}. As a generalisation of \pcc{}, it is \NPc{} but \textcite{Bonchi2012a}
present a modification of the \ccpivot{} algorithm that pick edges instead of nodes as pivots, and
grow clusters by adding monochromatic triangles. This gives an approximation factor of six times the
maximum degree of the graph. They also present a method when the number $k$ of clusters is fixed
beforehand, starting with an initial partition and then alternating between finding the majority
color of clusters and finding better clusters. An improved heuristic algorithm is given
in~\autocite{CCCheuristic16}. Unfortunately, the maximum degree of a graph can be
as large as $n$. However, \textcite{Anava2015} present constant factor approximations. Namely, they
show the problem can be reduced to classical \pcc{} by setting all edges incident to a node $u$ to
negative if they are not of the majority color of $u$. They then apply the regular \ccpivot{} and
show this gives an $11$-approximation to the original problem. Furthermore, they also write a linear
program and round it using the \regionGrow{} method to obtain an
approximation factor of $4$. \Textcite{multiChromatic15} extend this line of work to the case were a
single edge can carry a \emph{set} of labels and adapt their randomized algorithm so that the
approximation factor is multiplied by the size of the input label set.

@@

While in \pcc{}, each node is assigned to a single cluster, in other settings we may want to relax
this constraint. Given a complete weighted graph, \textcite{Bonchi2012} want to output a clustering
\cluster{} that minimizes the following cost: \[ \sum_{(u,v)\in E} \left| H(\cluster(u),
\cluster(v)) - w_{uv}\right|\] where $H$ is a similarity function between two sets of labels, chosen
here to be the Jaccard similarity or a $0/1$ indicator of nonempty intersection. These problems are
showed \NPc{} and approximated by a local search algorithm, iteratively optimizing the assignment of
one node while all others are fixed. As one of the demonstration on their theoretical work,
\textcite{WeightedTheta15} show a faster solution based on a weighted extension of the Lovász's
theta function, the corresponding geometric embedding of graphs and a solver derived from one-class
SVM, while \textcite{GeneticOCC14} propose a genetic algorithm to solve this problem. Finally,
\Textcite{StochasticCC13} also deals with overlapping clustering by relaxing the problem to a
stochastic setting and using \enquote{the Baum-Eagon inequality, which provides an effective
iterative scheme for maximizing polynomial functions in probability domains}.

@@

In classical \pcc{}, all nodes have an identical role, in the sense that they contribute equally to
the final objective in terms of (dis)agreements. Here we instead look at approaches where we either
add a local penalty to each in order to better control their behavior or where we altogether modify
the objective to focus on (dis)agreements at specific nodes.

@@

Given a function $f: \Rbb^n_{\geq 0} \rightarrow \Rbb$ verifying two elementary conditions, the
problem is then to find a fractional clustering $x$ minimizing $f(err(x))$. The classical \pcc{}
corresponds to setting $f(x) = \lhalf{}\ell^1(x)$ whereas the authors here are interested in Minimax
\pcc{} that arises by setting $f(x) = \ell^\infty(x)$. Minimizing the maximum number of
disagreements incurred by a single node is motivated by the example of recommendation systems: if
errors correspond to unsatisfying recommendations, we do not want a single user to suffer many
of them. Minimax \pcc{} is \NPc{} on both complete graphs and complete bipartite graphs but
by modifying the \regionGrow{} method, the authors respectively a $48$ and
$10$ approximation, the latter for the one-sided error (that only counts disagreements for the nodes
in one of the two clusters).
The idea is to chose pivots not randomly but by maximizing a given criteria and
to grow balls with a radius $\alpha$ computed numerically to optimize the approximation factor.
Interestingly, and in contrast with the classic \pcc{} situation, minimax \maxa{} is not easier than
minimax \mind{} and seems not to have a constant factor approximation, even on complete graphs.
Furthermore, these algorithms are deterministic, as opposed to many \pcc{} approximations, since
bounds on expected disagreements of an edge does not translate easily on their maximum.
\Textcite{Charikar2017} improve these two factors to $7$, using a simpler version of the algorithm
of \textcite{pmlr-v48-puleo16}. Namely, find the ball of radius $\nicefrac{1}{7}$ with the largest
number node and create a cluster from its center with a radius of $\nicefrac{3}{7}$. They also show
that on general weighted graphs, the LP has a large integrality gap of $\nicefrac{n}{2}$ yet they
combine it with a combinatorial approach to reach a $O(\sqrt{n})$ approximation. Finally, they
consider the complementary problem of maximizing the minimum number of agreements reach at a single
node, and provide a $\frac{1}{2+\epsilon}$ approximation.

@@

Finally, \textcite{mGeometricMean16} show that the Laplacians defined so far can be seen as
arithmetic means of the Laplacian $L^+$ of the positive subgraph $G^+=(V, E^+)$ and the signless
Laplacian $Q^-$ of the negative subgraph $G^-=(V, E^-)$, where $Q^- = D^- + A^-$. They suggest
instead to use a geometric mean defined for two positive matrices $A$ and $B$ as $A\#B =
A^{\shalf{}} \left(A^{-\shalf{}} BA^{-\shalf{}} \right)^{\shalf{}} A^{\shalf{}}$. This suggestion is
based on the fact that if $u$ is a common eigenvector of both $A$ and $B$ with eigenvalue $\lambda$
and $\mu$ respectively, then $u$ is an eigenvector of $A+B$ with eigenvalue $\lambda+\mu$ and an
eigenvector of $A\#B$ with eigenvalue $\sqrt{\lambda\mu}$. Therefore, the $k$ smallest eigenvalues
of the geometric mean Laplacian will be influenced by both smallest eigenvalues of $L^+$
(corresponding to assortative clusters in $G^+$) and of $Q^-$ (corresponding to disassortative
clusters in $G^-$), while this is not the case for the arithmetic mean of Laplacians.

@@

The clustering problem is often named community detection in the context of social networks, and
several methods developed by practitioners have been extended to signed graphs. While they do not
necessarily considered the \pcc{} objective, and especially not its optimum, we still give a brief
overview of them, as they tend to have been more tested experimentally. For instance, to find the
cluster of node $u$, \textcite{Yang2007} use a random walk approach on the positive subgraph $G^+$
to compute the probability of each node to reach $u$ in $T$ steps, sort the nodes accordingly and
then find a threshold  based on the number of disagreements.
The one node moves local heuristic that we described in the Physics-inspired paragraph
\vpageref{par:cc_physics} can also be formulated as genetic algorithms that simultaneously try to
minimize the number of disagreements and maximize a signed variant of the
modularity~\autocites{Li2013}{Amelio2013}. \Textcite{Anchuri2012} also consider these two objectives
by seeing them as eigenvalue problems and devise a iterative splitting procedure.
The overlapping community detection variant is considered by \textcite{Chen14}, who used a signed
probabilistic mixture model. Namely, an edge selects a pair of cluster $r,s$ with probability
$\omega_{rs}$ (where $r=s$ if the edge is positive and $r\neq s$ otherwise) and chooses its endpoints
$u$ and $v$ with probability $\theta_{ru}$ and $\theta_{sv}$. $\theta_{ru}$ is therefore the soft
membership of node $u$ to cluster $r$, and those parameters are estimated using the
expectation-maximization algorithm. The same model is extended to directed graphs by
\textcite{Jiang2015}, who strangely enough names it stochastic blockmodel, although the focus is
still on edge and not nodes.
In a similar spirit to \maxa{}$[k]$, \textcite{SignedGang} focus on finding $k$ subgraphs dense in
positive edges and densely connected by negative edges to each other. They dub such subgraph
\emph{Oppositive Cohesive Groups}, or more vividly \emph{Gangs in War}, and after formulating the
problem as a constrained quadratic optimization, they propose a faster iterative local search
heuristic. When $k=2$, these subgraphs are called antagonistic communities and a specific data
mining approach was proposed by \textcite{quasiGang16}.
% relaxed structural balance \autocite{Doreian2009} but used the same approach as \textcite{Early96}

>>>>

Bipartite graphs are an interesting special case for \pcc{}, as they often appear in the context of
recommendation systems, where users rate products positively or negatively, although in this setting
we cannot expect to have complete bipartite graphs in practice. The first results was given by
\textcite{Amit04}, who obtains an $11$-approximation for \mind{} by adapting the \regionGrow{} method.
The \ccpivot{} is adapted to the bipartite case by
\textcite{Bipartite12}, who prove it results in a randomized $4$-approximation (and provide a matching
deterministic approximation by rounding a LP). By using their idea of rounding the results of the LP
differently for positive, negative and in that case same-side absent edges, \textcite{Chawla2014}
bring down this approximation factor to $3$, even for $K\geq 2$-partite graphs. Through formulating the
\maxa{}$[k]$ problem as a bilinear maximization problem and computing a low-rank approximation of
the graph biadjacency matrix, \textcite{Asteris2016} obtain a efficient PTAS, that is a $(1-\delta)$
approximation running in time exponential in $k$ and $\delta^{-1}$ but linear in $n$. By an
appropriate choice of $k$, it is possible to use this PTAS to solve the general \maxa{} problem.
Beyond those results on \pcc{}, we further discuss bipartite signed graphs in \autoref{ssec:conc_rr}.

@@

In the so called \textsc{Chromatic}-\pcc{} setting, \enquote{positive} edges are now associated with
one of $L$ possible colors and the goal is to form clusters mostly made up of edges with the one same
color. Namely, a disagreement is now a negative edge between clusters or a within-cluster edge
whose color differs from the majority color of that cluster. This is motivated by edge-labeled graphs
in social networks, biology and citation networks and we will further discuss such applications in
\autoref{chap:vector}. As a generalisation of \pcc{}, it is \NPc{} but \textcite{Bonchi2012a}
present a modification of the \ccpivot{} algorithm that pick edges instead of nodes as pivots, and
grow clusters by adding monochromatic triangles. This gives an approximation factor of six times the
maximum degree of the graph. They also present a method when the number $k$ of clusters is fixed
beforehand, starting with an initial partition and then alternating between finding the majority
color of clusters and finding better clusters. An improved heuristic algorithm is given
in~\autocite{CCCheuristic16}. Unfortunately, the maximum degree of a graph can be
as large as $n$. However, \textcite{Anava2015} present constant factor approximations. Namely, they
show that the problem can be reduced to classical \pcc{} by setting all edges incident to a node $u$ to
negative if they are not of the majority color of $u$. They then apply the regular \ccpivot{} and
show this gives an $11$-approximation to the original problem. Furthermore, they also write a linear
program and round it using the \regionGrow{} method to obtain an
approximation factor of $4$. \Textcite{multiChromatic15} extend this line of work to the case were a
single edge can carry a \emph{set} of labels and adapt their randomized algorithm so that the
approximation factor is multiplied by the size of the input label set.

@@

While in \pcc{}, each node is assigned to a single cluster, in other settings we may want to relax
this constraint. Given a complete weighted graph, \textcite{Bonchi2012} want to output a clustering
\cluster{} that minimizes the following cost: \[ \sum_{(u,v)\in E} \left| H(\cluster(u),
\cluster(v)) - w_{uv}\right|\] where $H$ is a similarity function between two sets of labels, chosen
in their paper to be the Jaccard similarity or a $0/1$ indicator of nonempty intersection. These problems are
showed to be \NPc{}, and approximated by a local search algorithm, iteratively optimizing the assignment of
one node while all others are fixed. As one of the demonstration of their theoretical work,
\textcite{WeightedTheta15} show a faster solution based on a weighted extension of the Lovász's
theta function, the corresponding geometric embedding of graphs and a solver derived from one-class
SVM, while \textcite{GeneticOCC14} propose a genetic algorithm to solve this problem. Finally,
\Textcite{StochasticCC13} also deals with overlapping clustering by relaxing the problem to a
stochastic setting and using \enquote{the Baum-Eagon inequality, which provides an effective
iterative scheme for maximizing polynomial functions in probability domains}.

@@

In classical \pcc{}, all nodes have an identical role, in the sense that they contribute equally to
the final objective in terms of (dis)agreements. Here, we instead look at approaches where we either
add a local penalty to each in order to better control their behavior, or where we altogether modify
the objective to focus on (dis)agreements at specific nodes.

@@

Given a function $f: \Rbb^n_{\geq 0} \rightarrow \Rbb$ verifying two elementary conditions, the
problem is then to find a fractional clustering $x$ minimizing $f(err(x))$. The classical \pcc{}
corresponds to setting $f(x) = \lhalf{}\ell^1(x)$ whereas the authors here are interested in Minimax
\pcc{} that arises by setting $f(x) = \ell^\infty(x)$. Minimizing the maximum number of
disagreements incurred by a single node is motivated by the example of recommendation systems: if
errors correspond to unsatisfying recommendations, we do not want a single user to suffer many
of them. Minimax \pcc{} is \NPc{} on both complete graphs and complete bipartite graphs but
by modifying the \regionGrow{} method, the authors respectively a $48$ and
$10$ approximation, the latter for the one-sided error (that only counts disagreements for the nodes
in one of the two clusters).
The idea is to chose pivots not randomly but by maximizing a given criteria and
to grow balls with a radius $\alpha$ computed numerically to optimize the approximation factor.
Interestingly, and in contrast with the classic \pcc{} situation, minimax \maxa{} is not easier than
minimax \mind{} and seems not to have a constant factor approximation, even on complete graphs.
Furthermore, these algorithms are deterministic, as opposed to many \pcc{} approximations, since
bounds on expected disagreements of an edge does not translate easily on their maximum.
\Textcite{Charikar2017} improve these two factors to $7$, using a simpler version of the algorithm
of \textcite{pmlr-v48-puleo16}. Namely, find the ball of radius $\nicefrac{1}{7}$ with the largest
number node and create a cluster from its center with a radius of $\nicefrac{3}{7}$. They also show
that on general weighted graphs, the LP has a large integrality gap of $\nicefrac{n}{2}$. Yet they
combine it with a combinatorial approach to reach a $O(\sqrt{n})$ approximation. Finally, they
consider the complementary problem of maximizing the minimum number of agreements at a single
node, and provide a $\frac{1}{2+\epsilon}$ approximation.

@@

Finally, \textcite{mGeometricMean16} show that the Laplacians defined so far can be seen as
arithmetic means of the Laplacian $L^+$ of the positive subgraph $G^+=(V, E^+)$ and the signless
Laplacian $Q^-$ of the negative subgraph $G^-=(V, E^-)$, where $Q^- = D^- + A^-$. They suggest
instead to use a geometric mean, defined for two positive matrices $A$ and $B$ as $A\#B =
A^{\shalf{}} \left(A^{-\shalf{}} BA^{-\shalf{}} \right)^{\shalf{}} A^{\shalf{}}$. This suggestion is
based on the fact that if $u$ is a common eigenvector of both $A$ and $B$ with eigenvalue $\lambda$
and $\mu$ respectively, then $u$ is an eigenvector of $A+B$ with eigenvalue $\lambda+\mu$ and an
eigenvector of $A\#B$ with eigenvalue $\sqrt{\lambda\mu}$. Therefore, the $k$ smallest eigenvalues
of the geometric mean Laplacian will be influenced by both smallest eigenvalues of $L^+$
(corresponding to assortative clusters in $G^+$) and of $Q^-$ (corresponding to disassortative
clusters in $G^-$), while this is not the case for the arithmetic mean of Laplacians.

@@

The clustering problem is often named community detection in the context of social networks, and
several methods developed by practitioners have been extended to signed graphs. While they do not
necessarily considered the \pcc{} objective, and especially not its optimum, we still give a brief
overview of them, as they tend to have been more tested experimentally. For instance, to find the
cluster of node $u$, \textcite{Yang2007} use a random walk approach on the positive subgraph $G^+$
to compute the probability of each node to reach $u$ in $T$ steps, sort the nodes accordingly and
then find a threshold  based on the number of disagreements.
The one node move local heuristic that we described in the Physics-inspired paragraph
\vpageref{par:cc_physics} can also be formulated as genetic algorithms that simultaneously try to
minimize the number of disagreements and maximize a signed variant of the
modularity~\autocites{Li2013}{Amelio2013}. \Textcite{Anchuri2012} also consider these two objectives
by seeing them as eigenvalue problems and devise an iterative splitting procedure.
The overlapping community detection variant is considered by \textcite{Chen14}, who used a signed
probabilistic mixture model. Namely, an edge selects a pair of cluster $r,s$ with probability
$\omega_{rs}$ (where $r=s$ if the edge is positive and $r\neq s$ otherwise) and chooses its endpoints
$u$ and $v$ with probability $\theta_{ru}$ and $\theta_{sv}$. $\theta_{ru}$ is therefore the soft
membership of node $u$ to cluster $r$, and those parameters are estimated using the
expectation-maximization algorithm. The same model is extended to directed graphs by
\textcite{Jiang2015}, who strangely enough names it stochastic blockmodel, although the focus is
still on edge and not nodes.
In a similar spirit to \maxa{}$[k]$, \textcite{SignedGang} focus on finding $k$ subgraphs dense in
positive edges and densely connected by negative edges to each other. They dub such subgraph
\emph{Oppositive Cohesive Groups}, or more vividly \emph{Gangs in War}, and after formulating the
problem as a constrained quadratic optimization, they propose a faster iterative local search
heuristic. When $k=2$, these subgraphs are called antagonistic communities and a specific data
mining approach was proposed by \textcite{quasiGang16}.
% relaxed structural balance \autocite{Doreian2009} but used the same approach as \textcite{Early96}

### 2017-12-18 cc/conclusions.tex
pass over CC

	\item The basic analysis \autoref{prop:gtx_correct} shows that on any graph with $n$ nodes, the
		\gtx{} will perform at most $n$ collapses before terminating. However, as we mentioned
		\vpageref{par:number_of_iteration} at the end of \autoref{sub:gtx_algo}, we believe that this
		maximum number of collapses might be as low as $O(\log n)$. It turns out we were not able to
		prove this statement. This is unfortunate, for besides giving us guarantees on the algorithm
		runtime, this would also inform us about the stretch of the resulting tree. Indeed, let us
		consider the reverse direction in which the \gtx{} algorithm operates. That is, instead of a
		sequence of collapses transforming the original graph into a single node, we look at a sequence
		of expansions turning this single node into the original graph. Informally, the length of the
		longest path can only increase by a factor of five as each pair of nodes in $G_{t+1}$ expands
		into two connected stars in $G_{t}$.\footnote{More precisely, consider the edge $(u,v)$ in
		$G_{t+1}$. The two nodes are expanded into the two stars $s_u$ and $s_v$ in $G_t$, respectively
		with peripheral nodes $\{u_1, \ldots, u_k\}$ and $\{v_1, \ldots, v_\ell\}$ and center $c_u$ and
		$c_v$. In the worst case, there is now a path of length $5$ in $G_t$, \eg{} $(u_1, c_u, u_k,
		v_\ell, c_v, c_1)$.} Whereas the behavior of the average stretch is less straightforward, it is
		reasonable to expect that the smaller the number of expansions, the lower the stretch.

	\item As mentioned in \autoref{sec:troll_related}, \esp{} could be extended to weighted signed
		graphs. This is also relevant in undirected signed graphs. For instance, the signs might have
		been generated by thresholding an expensive symmetric similarity function. In that case, we
		might want to avoid extra evaluation of that function by predicting the signed weight of some
		new edges. A natural way to modify the \gtx{} algorithm is the following. When choosing the
		center of stars, pick the node with the current highest weighted degree. When choosing an edge
		to connect two center, pick among the edges with the lowest endpoints eccentricity the one with
		the lowest weight. What is less clear is to which extent such changes would affect the analysis.

	\item We wish we had more time to further explore \pcc{} under stability assumptions, especially
		as a way to handle the case where $K>2$. Recall that a clustering instance, made of a weighted
		graph and a partition objective, is \emph{$\alpha$-stable} (with $\alpha>1$) if its optimal
		partition remains the same whenever every weight $w_i$ is multiplied by a factor $c_i$ between
		$1$ and $\alpha$. Furthermore, we say that an algorithm is \emph{robust} if, given a clustering
		instance $\mathcal{I}$, it yields of the two following outcomes in polynomial time:
		\begin{enumerate}[(i),nosep]
			\item if $\mathcal{I}$ is $\alpha$-stable, returns the optimal solution of $\mathcal{I}$;
			\item if $\mathcal{I}$ is not $\alpha$-stable, either returns the optimal solution of
				$\mathcal{I}$ or reports that $\mathcal{I}$ is not $\alpha$-stable.
		\end{enumerate}
		This is a handy property because, in general, we cannot practically check the stability of an
		instance. Indeed, since we do not know the optimal solution, we cannot tell whether it changes
		or not under perturbations.

		As an example, let us consider the \minmc{} problem. Given a weighted undirected graph $G$ and a
		set of $k$ terminal nodes, the goal is to partition $G$ into $k$ clusters, each containing
		exactly one terminal, such that the total weight of edges across clusters is minimized. This
		bears some superficial similarity with \mmc{}. Recall from \autoref{ssub:cc_harness_approx} that
		\mmc{} requires us the find the lightest set of edges to cut in order to separate $k$ pairs of
		nodes.  Recall further that \mmc{} is equivalent to \pcc{}. As for \minmc{}, we can cast it as a
		\pcc{} problem~\autocite[Theorem 24]{Bansal2004}. Interestingly, there exists a robust
		algorithm for $2-\nicefrac{2}{k}$-stable instances of \minmc{}~\autocite{StableCC17}.  Under the
		assumption that graphs obeying our learning bias are $\alpha$-stable, for some $\alpha$
		depending of the graph irregularity, having such a stable algorithm for \mmc{} would be very
		valuable.  However, this might prove challenging. Indeed, \mmc{} is harder than \minmc{}, as
		illustrated by their respective approximation factor, $O(\log n)$ and less than
		$1.3$~\autocite{minmcApprox17}.

>>>>

	\item The basic analysis of \autoref{prop:gtx_correct} shows that on any graph with $n$ nodes, the
		\gtx{} will perform at most $n$ collapses before terminating. However, as we mentioned
		\vpageref{par:number_of_iteration} at the end of \autoref{sub:gtx_algo}, we believe that this
		maximum number of collapses might be as low as $O(\log n)$. It turns out we were not able to
		prove this statement. This is unfortunate, for besides giving us guarantees on the algorithm
		runtime, this would also inform us about the stretch of the resulting tree. Indeed, let us
		consider the reverse direction in which the \gtx{} algorithm operates. That is, instead of a
		sequence of collapses transforming the original graph into a single node, we look at a sequence
		of expansions turning this single node into the original graph. Informally, the length of the
		longest path can only increase by a factor of five as each pair of nodes in $G_{t+1}$ expands
		into two connected stars in $G_{t}$.\footnote{More precisely, consider the edge $(u,v)$ in
		$G_{t+1}$. The two nodes are expanded into the two stars $s_u$ and $s_v$ in $G_t$, respectively
		with peripheral nodes $\{u_1, \ldots, u_k\}$ and $\{v_1, \ldots, v_\ell\}$ and center $c_u$ and
		$c_v$. In the worst case, there is now a path of length $5$ in $G_t$, \eg{} $(u_1, c_u, u_k,
		v_\ell, c_v, c_1)$.} Whereas the behavior of the average stretch is less straightforward, it is
		reasonable to expect that the smaller the number of expansions, the lower the stretch.

	\item As mentioned in \autoref{sec:troll_related}, \esp{} could be extended to weighted signed
		graphs. This is also relevant in undirected signed graphs. For instance, the signs might have
		been generated by thresholding an expensive symmetric similarity function. In that case, we
		might want to avoid extra evaluation of that function by predicting the signed weight of some
		new edges. A natural way to modify the \gtx{} algorithm is the following. When choosing the
		center of stars, pick the node with the current highest weighted degree. When choosing an edge
		to connect two centers, pick among the edges with the lowest endpoints eccentricity the one with
		the lowest weight. What is less clear is to which extent such changes would affect the analysis.

	\item We wish we had more time to further explore \pcc{} under stability assumptions, especially
		as a way to handle the case where $K>2$. Recall that a clustering instance, made of a weighted
		graph and a partition objective, is \emph{$\alpha$-stable} (with $\alpha>1$) if its optimal
		partition remains the same whenever every weight $w_i$ is multiplied by a factor $c_i$ between
		$1$ and $\alpha$. Furthermore, we say that an algorithm is \emph{robust} if, given a clustering
		instance $\mathcal{I}$, it yields one of the two following outcomes in polynomial time:
		\begin{enumerate}[(i),nosep]
			\item if $\mathcal{I}$ is $\alpha$-stable, returns the optimal solution of $\mathcal{I}$;
			\item if $\mathcal{I}$ is not $\alpha$-stable, either returns the optimal solution of
				$\mathcal{I}$ or reports that $\mathcal{I}$ is not $\alpha$-stable.
		\end{enumerate}
		This is a handy property because, in general, we cannot practically check the stability of an
		instance. Indeed, since we do not know the optimal solution, we cannot tell whether it changes
		or not under perturbations.

		As an example, let us consider the \minmc{} problem. Given a weighted undirected graph $G$ and a
		set of $k$ terminal nodes, the goal is to partition $G$ into $k$ clusters, each containing
		exactly one terminal, such that the total weight of edges across clusters is minimized. This
		bears some superficial similarity with \mmc{}. Recall from \autoref{ssub:cc_harness_approx} that
		\mmc{} requires us to find the lightest set of edges to cut in order to separate $k$ pairs of
		nodes.  Recall further that \mmc{} is equivalent to \pcc{}. As for \minmc{}, we can cast it as a
		\pcc{} problem~\autocite[Theorem 24]{Bansal2004}. Interestingly, there exists a robust
		algorithm for $2-\nicefrac{2}{k}$-stable instances of \minmc{}~\autocite{StableCC17}.  Under the
		assumption that graphs obeying our learning bias are $\alpha$-stable, for some $\alpha$
		depending of the graph irregularity, having such a stable algorithm for \mmc{} would be very
		valuable.  However, this might prove challenging. Indeed, \mmc{} is harder than \minmc{}, as
		illustrated by their respective approximation factor, $O(\log n)$ and less than
		$1.3$~\autocite{minmcApprox17}.
